Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-07-24 Latex/journal_v1/V5/pr.tex
add bar and power

\begin{abstract}
Taking advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems which leads to increase flexibility, Openness, and reduce operational costs and allow them to add new capabilities to the network more quickly.
O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for a different types of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
According to the concept of network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
The limited fronthaul capacity and the restriction of end-to-end delay are considered in this problem.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is the mixed-integer non-linear programming that is tremendously difficult.
To solve the challenging problem, we broke it down into two different steps that the iterative algorithm solves it.
In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is carried out.
The proposed method (IAPPVO) is confirmed by the simulation results in a way that
the simulations illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm that is described in other papers.

@@

\section{Introduction} 
One of the goals of the fifth generation of wireless system is to achieve the desired QoS (such as rate, delay, power, ...) for different type of services. Network slicing is the best solution for this aim.
A network slice is an end-to-end logical network
which offers services with special needs. 
Multiple isolated network slices run, manage
,and work independently on the same infrastructure. There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections. 
Different type of services includes enhanced mobile broadband (eMBB) and ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network. Each type of service requires special slice of network based on its QoS
 \cite{shen2020ai,setayesh2020joint,popovski20185g}.

Recently, RAN virtualization attracts significant attention from  both industry and academia since it 
has remarkable benefits which leads to increase the flexibility and 
reduce operator costs
such as CAPEX and OPEX and also allow them to add new capabilities to the network more quickly.
In addition to RAN virtualization, openness and RAN intelligence are two other fundamental points that encourage Open Radio Access Network (O-RAN)
Alliance to establish O-RAN as a next generation of RAN systems. 
The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
CRAN, divides RAN into two parts radio remote head (RRH) and base band unit (BBU). 
More than one distributed RRHs can be connected to a centralized BBU which is named BBU-pool\cite{han2019research}.
Unlike previous generation of RAN that divide RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
Central Unit (O-CU).
O-RU is a logical node contains RF and lower PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC and RLC. In addition, the O-CU depicts the logical node contains two parts, which are O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP and
O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
RAN Intelligent Controller (RIC)- Near Real Time and O-Cloud. 
One of the necessities of new generation of wireless networks is its intelligence.
Based on the requirement of smart wireless network, O-RAN offers machine learning techniques.
The two logical nodes RIC-Non Real Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time implement the algorithms for network intelligence 
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.

To improve system performance in the fifth generation of telecommunications, the separation of network software and hardware elements has been done and introduced as network function virtualization (NFV), and virtual network functions (VNF) are system function blocks. The key idea of the implementation of NFV is 
to decouple software from physical hardware, dynamic scaling and the deployment of flexible network function. A usual NFV offer is to execute VNFs on a virtual machines or containers in a cloud system \cite{mijumbi2015network, luo2020online}.
As a result, some O-RAN components that includes user plane function (UPF) , O-CU, O-DU and RAN Intelligent Controller (RIC)-near real time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
\subsection{Related Works}
Network slicing is increasingly receiving research attention.
Many researcher, studied the problem of resource allocation in network slicing for multitenant cellular networks \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic},
dynamic network slicing in multitenant heterogeneous CRAN (H-CRAN) is considered. The process of allocating network resources to users is discussed. The network slicing scheme includes a higher level, which manages user acceptance control, user communication which includes radio unit association (RRH association to maximize user rates and allocate base band resource capacity), the allocation of BBU capacity and a lower level, which is the allocation of power and physical resource blocks (PRB) among users. 
In article \cite{xiang2020realization}, network slicing in the radio section is considered for fog or F-RAN structure, in which two network slices are set for hotspots and vehicle scenarios with related infrastructure. In \cite{elayoubi20195g,d2020toward} the implementation of RAN level slicing is discussed in mobile network operator (MNO). Also the problem of resource allocation is considered. 
Moreover, the challenges facing RAN slicing have also been explored, one of which involves designing and managing multiple slices in the shared infrastructure in an efficient manner while guaranteeing the agreed 
service level agreement (SLA) for each.

Multiplexing of eMBB and URLLC services on the same RAN and sharing the resources for these services is a challenging problem that many researchers pay attention to this topic. In \cite{setayesh2020joint,yang2020should}
the problem of resource allocation in the coexistence of these two services (URLLC and eMBB) is considered
based on their QoS. In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC is formulated and solved by deep reinforcement learning. In \cite{saggese2021power}
the problem of power minimization for these two type services (URLLC and eMBB) is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA). In \cite{korrai2020ran},
the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantee the latency, the service rate and the  maintenance of the reliability.

Virtualization technique for RAN and core is one of the interested topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation 
in C-RAN system with limited fronthaul capacity. The goal of this paper is to minimize the energy cost, with the system delay, fronthaul capacity and rate constraint. To guarantee delay for services, transmission and processing delay is modeled based on M/M/1 queuing theory. In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also the association of RRH to UE is considered and solved using novel methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in H-CRAN system is considered to maximize energy efficiency.
\subsection{Main Contribution}
The aim of this study is to jointly optimize VNF activation, power allocation, PRB allocation ,and O-RUs association to develop an isolated network slicing outline for different type of services in an O-RAN platform. In this paper, as  depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied.
The main contributions of this paper are summarized as follow:
\begin{itemize}
\item In this paper a network slicing model is depicted for three different type of services introduced in 5G (URLLC, eMBB and mMTC) and the problem of radio resource allocation and VNF activation is studied in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of O-RAN system for different type of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different type of services. We formulate the end-to end mean delay of system based on the activated VNFs and the throughput of each user.
We take into account the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
We model the interference of neighboring O-RU and formulate the accurate throughput
for different type of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is a mixed-integer non linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation and PRB association and the second-step O-RU association.
\item For the first-step, we reformulate and simplificate the main problem to find an upper and lower bound for number of activated VNFs and using lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second-step, the problem of O-RU association can be convert to a multiple knapsack problem and solved by Greedy algorithm.
\end{itemize}

@@

The rest of this paper is organized as follow. The system model and the problem formulation is described 
in Section \ref{systemmodel}. The details of our proposed resource management algorithm is 
introduced in Seection \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Section \ref{conc}, concludes the whole paper.

@@

   Minimum data rate for URLLC and mMTC &  10 bits/sec/Hz \\ 

@@

 Here we assume that services have the same priority. The figure, presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.

@@

    \includegraphics[scale = 0.4]{rate_ue1.eps}

@@

%Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
%The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{mmtcurllc.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
%  \label{fig:2}
%\end{figure}
%In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{sumRatePri.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
%  \label{fig:3}
%\end{figure}
In figure \ref{fig:4}, the number of activated VNF for two different mean service time of a one eMBB service is depicted vs. mean arrival time. This figure, presented that as the mean arrival rate increases, the number of activated VNF increases. Moreover, the number of activated VNFs for the mean service rate of $\mu = 1.6Mbps$ is less than the number of activated VNFs for mean service rate of $\mu  =  0.8Mbps$.

\begin{figure}
  \centering 
    \includegraphics[scale = 0.4]{vnfNum.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Number of activated VNF in each Service vs. Mean Arrival Rate(Mbps)}
  \label{fig:4}
\end{figure}

\section{Conclusion}\label{conc}
In this paper, we proposed the downlink of O-RAN system using network slicing for different types of 5G services (eMBB, mMTC and URLC). The goal of this paper is to obtain number of activated VNFs in each service, RU association, power and PRB allocation to maximize the sum-rate. The limited fronthaul capacity, and the mean end-to-end delay for each service is considered. 
The problem is mixed-integer non-linear programming that is solved by the iterative algorithm.
The performance of our proposed method (IAPPVO) is compared with baseline scheme and FBDR in \cite{lee2018dynamic}.   
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}

>>>>

\begin{abstract}
Taking advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems which leads to increase flexibility, Openness, and reduce operational costs and allow them to add new capabilities to the network more quickly.
O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different types of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
According to the concept of network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
The limited fronthaul capacity and the restriction of end-to-end delay are considered in this problem.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is the mixed-integer non-linear programming that is tremendously difficult.
So we broke it down into two different steps that the iterative algorithm solves it.
In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is carried out.
The proposed method (IAPPVO) is confirmed by the simulation results so that the simulations illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources and the FBDR algorithm described in other papers.

@@

\section{Introduction} 
One of the fifth-generation goals of the wireless system is to achieve the desired QoS (such as rate, delay, power, ...) for different types of services. Network slicing is the best solution for this aim. A network slice is an end-to-end logical network that offers services with special needs.  
Multiple isolated network slices run, manage, and work independently on the same infrastructure. There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections. 
Different type of services includes enhanced mobile broadband (eMBB), and ultra-reliable low latency communications (URLLC), and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network. Each type of service requires a particular slice of network based on its QoS
\cite{shen2020ai,setayesh2020joint,popovski20185g}.

Recently, RAN virtualization attracts significant attention from industry and academia since it has remarkable benefits that increase flexibility and reduce operating costs such as CAPEX and OPEX and allow them to add new capabilities to the network more quickly. In addition to RAN virtualization, openness and RAN intelligence are two other fundamental points that encourage the Open Radio Access Network (O-RAN) Alliance to establish O-RAN as the next generation of RAN systems.

The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN), and it takes advantage of both. CRAN divides RAN into two parts radio remote head (RRH) and baseband unit (BBU).  More than one distributed RRHs can be connected to a centralized BBU, which is named BBU-pool \cite{han2019research}. 
Unlike the previous generation of RAN that divides RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU). 
O-RU is a logical node that contains RF and lowers PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC, and RLC.
 In addition, the O-CU depicts the logical node contains two parts, which are the O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP, and O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to a radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
RAN Intelligent Controller (RIC)- Near Real-Time and O-Cloud. 
One of the necessities of the new generation of wireless networks is its intelligence.
Based on the requirement of an intelligent wireless network, O-RAN offers machine learning techniques. The two logical nodes RIC-Non Real-Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time, implement the algorithms for network intelligence 
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML,lin2021toward}.

The separation of network software and hardware elements has been done and introduced as network function virtualization (NFV), and virtual network functions (VNF) are system function blocks. This technology improves the system performance in the fifth generation of telecommunications. 
The key idea of the implementation of NFV is to decouple software from physical hardware, dynamic scaling, and the deployment of flexible network functions. A usual NFV offer is to execute VNFs on virtual machines or containers in a cloud system \cite{mijumbi2015network, luo2020online}.
As a result, some O-RAN components that include user plane function (UPF), O-CU, O-DU, and RAN Intelligent Controller (RIC)-near real-time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
\subsection{Related Works}
Network slicing is increasingly receiving research attention.
Many researchers studied the problem of resource allocation in network slicing for multitenant cellular networks \cite{feng2020dynamic,lee2018dynamic,lee2016new}.
In \cite{lee2018dynamic}, dynamic network slicing in multitenant heterogeneous CRAN (H-CRAN) is considered. The process of allocating network resources to users is discussed. The network slicing scheme includes a higher level, which manages user acceptance control, user communication includes radio unit association (RRH association to maximize user rates and allocate baseband resource capacity), the allocation of BBU capacity, and a lower level, which is the allocation of power and physical resource blocks (PRB) among us
In the article, \cite{xiang2020realization}, network slicing in the radio section is considered for fog or F-RAN structure, in which two network slices are set for hotspots and vehicle scenarios with related infrastructure. In \cite{elayoubi20195g,d2020toward} the implementation of RAN level slicing is discussed in mobile network operator (MNO). Also, the problem of resource allocation is considered.  Moreover, the challenges facing RAN slicing have also been explored, one of which involves designing and managing multiple slices in the shared infrastructure in an efficient manner while guaranteeing the agreed service level agreement (SLA) for each.

Multiplexing eMBB and URLLC services on the same RAN and sharing the resources for these services is challenging because many researchers pay attention to this topic.
In \cite{setayesh2020joint,yang2020should} the problem of resource allocation in the coexistence of these two services (URLLC and eMBB) is considered based on their QoS. 
In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC is formulated and solved by deep reinforcement learning.
 In \cite{saggese2021power} the problem of power minimization for these two types of services (URLLC and eMBB) is presented for non-orthogonal multiple access (NOMA) and orthogonal multiple access (OMA).
 In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees the latency, the service rate, and the maintenance of reliability.

Virtualization technique for RAN and core is one of the exciting topics.  
In \cite{SystemCostMinimization,guo2016exploiting}, the authors solve the problem of obtaining beamforming and VMs activation in a C-RAN system with limited fronthaul capacity. 
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint. 
Also, Transmission and processing delay are modeled based on M/M/1 queuing theory to guarantee delay for the services.
 In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to UE is considered and solved using novel methods.
In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
\subsection{Main Contribution}
This study aims to optimize VNF activation, power allocation, PRB allocation, and O-RUs association to develop an isolated network slicing outline for different types of services in an O-RAN platform. In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the ORAN system is studied. The main contributions of this paper are summarized as follow:
\begin{itemize}
\item In this paper, a network slicing model is depicted for three different types of services introduced in 5G (URLLC, eMBB, and mMTC). The problem of radio resource allocation and VNF activation is studied in this paper in the O-RAN architecture.
We formulate the problem of baseband resource allocation to maximize the weighted throughput of the O-RAN system for a different types of services with specific QoS. 
\item The desired QoS conditions such as delay and throughput are considered for different types of services. We formulate the end-to-end mean delay of the system based on the activated VNFs and each user's throughput.
We take into account the limited fronthaul capacity and accurately obtain the power and the capacity of each O-RU based on the quantization noise.
We model the interference of neighboring O-RU and formulate the actual throughput
for different types of services. We model the throughput of URLLC and mMTC based on their short packet transmission.
\item The main problem is mixed-integer non-linear programming that is extremely difficult to solve.
We perform a two-step iterative algorithm to solve it.
The two-step iterative algorithm is presented for the resource management framework with the first-step VNF activation, power allocation, PRB association, and the second-step O-RU association.
\item We reformulated and simplified the main problem for the first step to find an upper and lower bound for the number of activated VNFs and use lagrangian function and KKT conditions to find optimal power and PRB allocation.
For the second step, the problem of O-RU association can be converted to a multiple knapsack problem and solved by the Greedy algorithm.
\end{itemize}

@@

The rest of this paper is organized as follows. The system model and the problem formulation are described in Section \ref{systemmodel}. The details of our proposed resource management algorithm are introduced in Section \ref{proAlg}. In Section \ref{NE}, numerical results are provided to evaluate the performance of the proposed algorithm. Section \ref{conc}, concludes the whole paper.

@@

   Minimum data rate for URLLC and mMTC &  6 bits/sec/Hz \\ 

@@

Here, we did not consider the priority. The figure, presented that the proposed algorithm is $18.6\%$ higher than the baseline scheme.

@@

    \includegraphics[scale = 0.5]{rate_ue1.eps}

@@

%Assume we have two type of services (URLLC and mMTC). In figure \ref{fig:2} and \ref{fig:3}, the aggregate throughput (by considering the priority factor 
%($\sum_s \sum_i \delta_s \bar{R}_{{u(s,i)}}$)) is depicted for two services URLLC and mMTC. Here we consider 4 UEs in each service. The other parameter is shown in table \ref{table:1a}.
%The figure \ref{fig:2}, presented that by increasing the priority factor for URLLC, more resources is allocated to this service and the aggregate throughput of this service is increased and vice verse.
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{mmtcurllc.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput for mMTC and URLLC vs. Priority of URLLC }
%  \label{fig:2}
%\end{figure}
%In figure \ref{fig:3}, the total sum rate of URLLC and mMTC is shown vs. priority of URLLC. It is shown that the proposed method is much better than the baseline scheme. 
%\begin{figure}
%  \centering 
%    \includegraphics[scale = 0.4]{sumRatePri.eps}
%    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
%    %\includegraphics[width=\textwidth]{finalDraw.pdf}
%  \caption{Aggregate Throughput of all services vs. Priority of URLLC}
%  \label{fig:3}
%\end{figure}
In figure \ref{fig:4}, the number of activated VNF for the five different mean service time of a one URLLC service is depicted vs. mean arrival time for 12 UEs. This figure, presented that as the mean arrival rate increases, the number of activated VNF increases. Moreover, the number of activated VNFs decreased when the mean service rate increases.

\begin{figure}
  \centering 
    \includegraphics[scale = 0.5]{vnfNum1.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Number of activated VNF in each Service vs. Mean Arrival Rate(Mbps)}
  \label{fig:4}
\end{figure}

In figure \ref{fig:5}, the aggregate throughput is depicted vs. the maximum power of UE for three different instances of eMBB service using proposed method. Here, we suppose that we have 12 UEs in each service.  We assume that these three services require 5bits/sec/Hz, 10bits/sec/Hz, and 15bits/sec/Hz.
In addition, We suppose that each O-RU can transmit three times of the maximum power of UE. As you can see in the figure, increasing the maximum power increases the aggregate throughput.

\begin{figure}
  \centering 
    \includegraphics[scale = 0.5]{RatePower1.eps}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Aggregate Throughput for eMBB vs. Maximum Transmit power}
  \label{fig:5}
\end{figure}

\section{Conclusion}\label{conc}
This paper proposed the downlink of the O-RAN system using network slicing for different types of 5G services (eMBB, mMTC, and URLC). Also, the paper aims to obtain the number of activated VNFs in each service, RU association, power, and PRB allocation to maximize the sum rate. The limited fronthaul capacity and the mean end-to-end delay for each service are considered.  The problem is mixed-integer non-linear programming that is solved by the iterative algorithm. The performance of our proposed method (IAPPVO) is compared with the baseline scheme and FBDR in \cite{lee2018dynamic}.  
\bibliography{ref}
\end{document}
